---
title: "Github Users Around the World"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    highlight: tango
    theme: journal
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading data, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls())

# load packages
for (pkg in c("tidyverse", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi",  "dplyr", "leaflet", "leaflet.extras")) {library(pkg, character.only = TRUE)}


# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the ctrs_extra data from github data 
city_clean_final <- dbGetQuery(conn, "SELECT *
                              FROM gh.sna_ctr_city_codes")

# disconnect from postgresql database 
dbDisconnect(conn)


#https://coolors.co/232d4b-2c4f6b-0e879c-60999a-d1e0bf-d9e12b-e6ce3a-e6a01d-e57200-fdfdfd
uva_color_palette <- 
c("#232D4B", #space cadet
  "#2C4F6B", #indigo dye
  "#0E879C", #blue munsell
  "#60999A", #cadet blue
  "#D1E0BF", #tea green
  "#D9E12B", #pear
  "#E6CE3A", #citrine
  "#E6A01D", #marigold
  "#E57200" #princeton orange
)

```

We conduct analysis on github users' geographic location, which is extracted from the user profile. We ackowledge  `r round(sum(is.na(ctrs_extra$cc_multiple) | is.na(ctrs_extra$city))/nrow(ctrs_extra) * 100, digits = 2)` % missing geographic information (country and city name), which leaves us with `r sum(!is.na(ctrs_extra$cc_multiple) & !is.na(ctrs_extra$city))` github users in our analysis.
```{r clean citycode, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#aggregate by continent
city_clean_final_aggregate_continent<- city_clean_final%>%
  group_by(c_continent_name)%>%
  summarize(ttl_users = n(), `percent (%)` = round(ttl_users/nrow(city_clean_final)*100, digits = 2))%>%
  arrange(desc(ttl_users))

#aggregate by country
city_clean_final_aggregate_country <- city_clean_final%>%
  group_by(c_country_name)%>%
  summarize(ttl_users = n())%>%
  arrange(desc(ttl_users))
#city_clean_final_aggregate_country$country_code <- gsub(" ", "", city_clean_final_aggregate_country$country_code, fixed = TRUE)


#aggregate by U.S. state
city_clean_final_us <- city_clean_final%>%
  filter(c_country_name == "US")
check <- city_clean_final_us%>%
  group_by(raw_city, c_geo_code)%>%
  summarize(N=n())%>%
  group_by(raw_city)%>%
  summarize(N=n())%>%
  mutate(is.dup = if_else(N >1, T,F))
table(check$is.dup)
453/(453 + 3199)
table(is.na(city_clean_final_us$raw_state))

#aggregate by city
city_clean_final_aggregate <- city_clean_final%>%
  group_by(c_city_code, c_country_name)%>%
  summarize(ttl_users = n(), lat = mean(raw_lat), long = mean(raw_long))%>%
  arrange(-ttl_users)

city_clean_final_aggregate$city <- str_extract(city_clean_final_aggregate$c_city_code,"_(.*)_") 
city_clean_final_aggregate$city <- gsub("_", "", city_clean_final_aggregate$city, fixed = TRUE)
city_clean_final_aggregate$city<- sapply(city_clean_final_aggregate$city,CapStr)

city_clean_final_aggregate$city_country <- paste(city_clean_final_aggregate$city, city_clean_final_aggregate$c_country_name, sep = ", ")


top_city_vector <- as.vector(city_clean_final_aggregate[1:10,]$c_city_code)

city_clean_final_aggregate <- city_clean_final_aggregate%>%
  mutate(top_city = if_else(c_city_code %in% top_city_vector, "topcity", "not topcity"))
```


# Top Continents are Github Users Located 
North America is the continent that has the highest number of github users, following by Europe, and Asia.
```{r fig.width=8, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gh_continent<- city_clean_final_aggregate_continent%>%
  arrange(desc(ttl_users))

gh_continent$Continent_Name <- factor(gh_continent$c_continent_name, levels = gh_continent$c_continent_name[order(gh_continent$ttl_users)])

ggplot(gh_continent, aes(x = Continent_Name, y = ttl_users, fill = ttl_users))+
  geom_bar(stat = "identity")+ 
  scale_fill_continuous(low = uva_color_palette[5], high=uva_color_palette[8])+
  labs(title = "Continents where Github users are located", x = "continent", y = "total number of users", fill = "total number \n of users")+
  theme_bw() 
```

# Top Countries Where Github Users are Located
United States is the country that has the highest number of github users, following by China, United Kingdom, and India.
```{r fig.width=9, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gh_country <- city_clean_final_aggregate_country%>%
  arrange(desc(ttl_users))%>%
  top_n(10, ttl_users)

gh_country$c_country_name <- factor(gh_country$c_country_name, levels = gh_country$c_country_name[order(gh_country$ttl_users)])

ggplot(gh_country, aes(x = c_country_name, y = ttl_users, fill = ttl_users)) +
  geom_bar(stat = "identity")+ 
  scale_fill_continuous(low = uva_color_palette[5], high=uva_color_palette[8])+
  labs(title = "Countries where Github users are located", x = "country", y = "total number of users", fill = "total number \n of users") +
  theme_bw()
```


# Top Cities Where Github Users are Located
San Francisco (US) is the city that has the highest number of github users, following by London (UK), New York (US), Moscow (Russia), and Beijing (China).
```{r fig.width=11, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gh_city <- city_clean_final_aggregate%>%
  arrange(-ttl_users)%>%
 # top_n(10, ttl_users)%>%  #don't know why this code doesn't work
  filter(ttl_users >= 6651) 

gh_city$city_country <- str_replace_all(gh_city$city_country, fixed(","), "\n") 


gh_city$city_country <- factor(gh_city$city_country, levels = gh_city$city_country[order(gh_city$ttl_users)])
# NOTE ::: Could you please shorten the labels for the USA and Russia cities 

ggplot(gh_city, aes(x = city_country, y = ttl_users, fill = ttl_users))+
  geom_bar(stat = "identity")+ 
  scale_fill_continuous(low = uva_color_palette[5], high=uva_color_palette[8])+
  labs(title = "Countries where Github users are located", x = "city", y = "total number of users", fill = "total number \n of users") +
  theme_bw()
```

# City-level Interactive map
In this map, the size of the circle indicates the number of github users in each city. You can zoom in and hover over the circle to see how many users are in that city. You can also type in the city that you are interested in.
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#In this map, the color of the circle indicates the number of github users in each city, still under development.
city_clean_final_aggregate_top <- city_clean_final_aggregate%>%
  filter(ttl_users > 10)%>%
  mutate(ttl_users_t = log(ttl_users), perc = ttl_users_t/max(ttl_users_t))

pal <- colorFactor(
  palette = c(uva_color_palette[4], uva_color_palette[8]),
  levels = c( "not topcity", "topcity")
)


#ttl user indicated by size
city_clean_final_aggregate%>%
#  mutate(ttl_users_exp = exp(ttl_users)^(1/3))%>%
  leaflet()%>%
  addTiles()%>%
  addSearchOSM()%>%
  addReverseSearchOSM()%>%
  clearMarkers()%>%
  addResetMapButton()%>%
  addCircleMarkers(
    lng = ~long , 
    lat = ~lat, 
    label = ~ paste(city_country,", ", ttl_users, " user(s)", sep = ""),
    radius = ~ttl_users^(1/3), 
    color  = ~pal(top_city))%>% 
  addLegend(pal = pal, values = c( "not topcity", "topcity"))
```

